A generalized definition of multidimensional item response theory parameters

### 2024-04-03 output/paper_draft/paper_M2PLM_parameters.Rmd
Corrects minor erratum

Let $`r TEST_SPACE`$ be the vector space made up by
the set of $`r DISCR_VECTOR`$ vectors,
with the sum and product by a scalar operations as in $`r REAL_N_SPACE`$.
Consider also an orthonormal basis $`r TEST_SPACE_STD_BASIS`$
in $`r TEST_SPACE`$, such that $`r DISCR_STD_COORDS_ALT_EQ`$.
Since the response probability to the `r MODEL_ACRONYM`,
given by \@ref(eq:M2PL-formulation), must be invariant with respect to
the change of basis expressed in \@ref(eq:change-basis),
we must define the coordinates $`r DISCR_STD_COORDS`$ of the parameter vector
$`r DISCR_VECTOR`$ in the orthonormal basis $`r TEST_SPACE_STD_BASIS`$,
such that $`r INVARIANCE_EQ`$.
If we assume that $`r DISCR_VECTOR`$ exists in vector space $`r TEST_SPACE`$,
with coordinates $`r DISCR_COORDS`$ in basis $`r TEST_SPACE_BASIS`$,
then we must define $`r DISCR_COORDS`$ such that

@@

In the test space we have that

@@

Applying Proposition 1,

>>>>

Let $`r TEST_SPACE`$ be the vector space made up by
the set of $`r DISCR_VECTOR`$ vectors,
with the sum and product by a scalar operation as in $`r REAL_N_SPACE`$.
Consider also an orthonormal basis $`r TEST_SPACE_STD_BASIS`$
in $`r TEST_SPACE`$, such that $`r DISCR_STD_COORDS_ALT_EQ`$.
Since the response probability to the `r MODEL_ACRONYM`,
given by \@ref(eq:M2PL-formulation), must be invariant with respect to
the change of basis expressed in \@ref(eq:change-basis),
we must define the coordinates $`r DISCR_STD_COORDS`$ of the parameter vector
$`r DISCR_VECTOR`$ in the orthonormal basis $`r TEST_SPACE_STD_BASIS`$,
such that $`r INVARIANCE_EQ`$.
If we assume that $`r DISCR_VECTOR`$ exists in vector space $`r TEST_SPACE`$,
with coordinates $`r DISCR_COORDS`$ in basis $`r TEST_SPACE_BASIS`$,
then we must define $`r DISCR_COORDS`$ such that

@@

We have that

@@

Applying Proposition 1, in the test space $`r TEST_SPACE`$, we get
